---
title: "**Introduction to R**"
institute: "**Business school,Nanjing University**"
author: "Jing Bu"
date: "10/9/2018"
header-includes:
    \usepackage{ctex}
    \usepackage{color}
#output: 
#  beamer_presentation:
documentclass: ctexart
output:
  rticles::ctex:
     fig_caption: yes
     number_sections: yes
     toc: yes
classoption: "hyperref,"
#    colortheme: dolphin
#    fonttheme: professionalfonts
#    latex_engine: xelatex
#    theme: CambridgeUS
#    toc: false
#    incremental: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Getting Started With R 

- Not only a statistical programming language, but a computing environment for statistical computing and graphics.
- Powerful Programming and Extending Capability 
- Multiple Platforms
- Very excellent graphics 
- A big but not a determinate advantage:
  FREE 
  Open Source



\includegraphics{picture21.png}



## Installing R 

- The first thing you have to do to use R is to download it from here:[R](http://www.r-project.org)

- Choose the nearest mirror in China

 1. Tsinghua
 <https://mirrors.tuna.tsinghua.edu.cn/CRAN/>
 2. USTC
 <https://mirrors.ustc.edu.cn/CRAN/>
 3. LanZhou
 <https://mirror.lzu.edu.cn/CRAN/>
 4. Xiamen
 <http://mirrors.xmu.edu.cn/CRAN/>
 


## Using IDE: RStudio

- The most popular IDE for R 
- Also Free(for basic version)
- Combine with \texttt{Markdown} and  \texttt{Latex} to make scientific writings or presentation easier
- Download it from here: [RStudio](https://www.rstudio.com/products/rstudio/download/)



## Using R as \texttt{Stata}: Packages

- Many researchers provide their own R programs through the R project
webpage. 
- Many packages are already preinstalled in the basic R installation.
- They can be directly activated from RStudio.
- Or they are activated by issuing a command in the Console.
```{r install, echo=TRUE}
#install.packages("foreign",repos = "http://mirrors.ustc.edu.cn/CRAN/")
```



## Where to get help

- The online help in R describes all basic R commands as well as commands in active packages. 
- search the online help from the Help pane in RStudio.
- Alternatively, using the command

```{r help, echo=TRUE}
?load
# or
help("load")
# or
??load
# or
help.search("read")
```


\includegraphics{picture22.png}



# Basic data Management in R

##  Opening and Saving Data: Working directory
- R will look for data or save data in the drive and working directory.
- The working directory is specified depending on the operation system
```{r, echo=TRUE}
getwd()
```


## Changing the working directory

```{r,echo=TRUE}
setwd("/Users/admin/Desktop/teaching assiatant/Econometrics/teaching assistant slides/R")
getwd()
```


##  Importing Data: From STATA

- R will look for data or save data in the drive and working directory.
- The working directory is specified depending on the operation system
- imports data from STATA



(version<=12):
```{r stata12, echo=TRUE,message=FALSE,results='hide'}
library("foreign")
caschool <- read.dta("/Users/admin/Desktop/teaching assiatant/Econometrics/teaching assistant slides/R/caschool.dta")
cars_data <- read.dta("/Users/admin/Desktop/teaching assiatant/Econometrics/teaching assistant slides/R/caschool.dta")
```


##  Importing Data: From CSV
```{r csv, echo=TRUE,message=FALSE,results='hide'}
caschool_csv <- read.csv("/Users/admin/Desktop/teaching assiatant/Econometrics/teaching assistant slides/R/caschool.csv")
```


## Summary the Data
```{r cars_summary, echo = TRUE}
summary(cars_data)
```


## Variables

```{r dplyr, include=FALSE}
#install.packages("dplyr")
library(dplyr)

```
```{r name, echo=TRUE}
#install.packages("dplyr", repos = "http://mirrors.ustc.edu.cn/CRAN/")
names(cars_data)
```
- https://www.rdocumentation.org/

## Variables

```{r small, echo=TRUE,message=FALSE,results='hide'}
cars_data_small <- select(cars_data,observat,testscr,str,expn_stu,el_pct)

```


##  Data Manipulation

- generate new variable
```{r data, echo=TRUE}
cars_data_small$logexp <- log(cars_data$expn_stu)
cars_data_small$el_high <- cars_data$el_pct
head(cars_data_small)
```


## Descriptive Statistics

- summary a variable
```{r summary, echo=TRUE}
summary(cars_data_small$testscr)
```


- if the dataframe is attached, simply
```{r sum2, echo=TRUE}
attach(cars_data_small)
summary(testscr)
detach(cars_data_small)
```


# Plot

## Scatter Plot

- Draw a scatter plot of the variable testscr against str:
```{r scatter, echo=TRUE}
attach(cars_data_small)
plot(str, testscr)
abline(lm(testscr ~ str , data = cars_data_small),col = "red")
```


\includegraphics{picture23.png}



## ggplot2

```{r scatter2,echo=TRUE,message=FALSE,warning=FALSE,error=FALSE}
library("ggplot2")
ggplot(data =cars_data_small,aes(x=str, y=testscr)) +
geom_point(shape=1) + # Use hollow circles
geom_smooth(method=lm) # Add linear regression line
```


## A kdensity distribution of income

```{r kensity1, echo=TRUE}
cars_data$inc <- with(cars_data,avginc >=15)
ggplot(cars_data,aes(x=avginc))+
geom_density(fill="grey",color ="blue")+
geom_vline(xintercept = 15)
```


```{r kensity2, echo=TRUE}
cars_data$logavginc <- log(cars_data$avginc)
ggplot(cars_data,aes(x=logavginc))+
geom_density(fill="grey",color ="blue")
```

## extra image

```{r image, echo=TRUE,collapse=FALSE}
library(readxl)
image <- read_excel("/Users/admin/Desktop/teaching assiatant/Econometrics/teaching assistant slides/R/image.xlsx")
attach(image)
opar<-par(no.readonly = TRUE)
par(pch=18,lwd=2)
par(cex=1,cex.axis=1,cex.lab=1)
par(font=1,font.axis=1,font.lab=1)
par(pin=c(5,2))
plot(year,rate,type="o",bty="l",ann=FALSE,xaxt="n",yaxt="n",xlim=c(2005,2018),ylim=c(70,85))
title(xlab="year",ylab="usage of capacity")
axis(1,at=year,tck=0.02,cex.axis=0.95,las=0)
axis(2,tck=0.02,las=2,cex.axis=1)
par(opar)
```


\includegraphics{picture24.png}



# OLS Regression

```{r reg, echo=TRUE}
fm1 <- lm(testscr ~ str,data = cars_data_small)
summary(fm1)
```


## OLS Regression 2
```{r reg2, echo=TRUE}
fm2 <- lm(testscr ~ str,data = cars_data)

summary(fm2)
```


# T-test in R

## single sample

- t-test for scores
```{r t-test, echo=TRUE}
summary(cars_data_small$testscr)
```


```{r t-test1, echo=TRUE}
t.test(cars_data_small$testscr,alternative = "two.sided",mu = 650)
```


- Construct t-Statistics
```{r t-test2, echo=TRUE}
randT <- rt(30000,df=NROW(testscr)-1) # build a distribution
scoreTtest <- t.test(cars_data_small$testscr,alternative = "two.sided",mu = 650)
ggplot(data.frame(x=randT)) +
geom_density(aes(x=x),fill = "grey",color ="blue") +
geom_vline(xintercept = scoreTtest$statistic) +
geom_vline(xintercept = mean(randT) + c(-2,2)*sd(randT),linetype = 2)
```



```{r t-test3, echo=TRUE}
#attach(cars_data_small)
#t.test(testscr~el_high,data = cars_data_small)
```


# R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.